Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete

### 2015-06-17 main/LMCS.tex
Wording tweak
added reviews

The idea of the present work is to look at proof equivalence through the lens of computational
complexity, and use this to settle the question of whether there can be canonical proof nets
for \capsabbrev{mll} with units. The canonical proof nets for \capsabbrev{mll} without units
give an efficient decision procedure for proof equivalence: to decide whether two such proofs
are equivalent, it is sufficient to translate both to proof nets and compare the proof nets
for equality.

The corresponding decision procedure for \capsabbrev{mll} \emph{with} units is shown to be
\capsabbrev{pspace}-complete, which is generally supposed to preclude the existence of a
polynomial-time algorithm for this problem. So there can be no canonical proof nets in the
usual sense: if the proof nets are syntactically equal just when their corresponding proofs
are equivalent, then the translation from proofs to proof nets must be intractable.

@@

\newpage

%\acks

We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees for their constructive observations.

>>>>

The idea of the present work is to look at proof equivalence through the lens of computational
complexity, and use this to settle the question of whether there can be canonical proof nets
for \capsabbrev{mll} with units. The canonical proof nets for \capsabbrev{mll} without units
give an efficient decision procedure for proof equivalence: to decide whether two such proofs
are equivalent, it is sufficient to translate both to proof nets and compare the proof nets
for equality.
%
We show that the corresponding decision procedure for \capsabbrev{mll} \emph{with} units is
\capsabbrev{pspace}-complete, which is generally supposed to preclude the existence of a
polynomial-time algorithm for this problem. So there can be no canonical proof nets in the
usual sense: if the proof nets are syntactically equal just when their corresponding proofs
are equivalent, then the translation from proofs to proof nets must be intractable.

@@
